\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{hyperref}
\title{Graph-Theoretic Discovery of Quantum Error Correction Codes with Enhanced Fault-Tolerance\\\large Phase-1 Computational Report}
\author{Codex Research Automation Team\\OpenAI Computational Methods Lab}
\date{\today}
\begin{document}
\maketitle

\begin{abstract}
We implement a reproducible phase-1 pipeline for automated graph-theoretic stabilizer-code discovery.
The framework constructs candidate symplectic stabilizer matrices from graph adjacencies, checks commutation constraints over $\mathbb{F}_2$, extracts logical operators, estimates distances, and stores candidates in SQLite.
We further provide a Monte Carlo depolarizing-noise simulation module for preliminary logical-error sweeps.
This report documents the architecture, algorithms, and validation tests required to scale toward publication-grade exhaustive experiments.
\end{abstract}

\section{Methods}
Given an undirected graph with adjacency matrix $A \in \{0,1\}^{n\times n}$, we construct
\[
S = \begin{bmatrix}A & I\\ I & A\end{bmatrix}
\]
and verify commutativity using $S\Omega S^\top = 0 \pmod 2$ with canonical symplectic form $\Omega$.
Logical operators are extracted from the commutant nullspace and filtered modulo stabilizer row span.

\section{Implementation}
Code is provided under \texttt{src/quantum\_codes\_discovery/} including modules for GF(2) linear algebra, graph search, stabilizer construction, threshold sweeps, and database persistence.

\section{Current Status}
This repository revision is an initial, test-covered implementation suitable for iterative scaling.
It does not yet claim the full exhaustive search, Lean formalization, or publication-scale Monte Carlo budgets.

\end{document}
